### 2023-10-18 Proposal/ProjectProposal.tex

\documentclass[12pt, letterpaper]{article}
%\documentclass[12pt, letterpaper, titlepage]{article}

\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{colorlinks = true, linkcolor = blue, citecolor=blue, urlcolor = blue}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{lipsum}
\usepackage[square,numbers]{natbib}
\bibliographystyle{abbrvnat}

\usepackage[]{lineno}
\linenumbers*[1]
% %% patches to make lineno work better with amsmath
\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
 \expandafter\let\csname old#1\expandafter\endcsname\csname #1\endcsname
 \expandafter\let\csname oldend#1\expandafter\endcsname\csname end#1\endcsname
 \renewenvironment{#1}%
 {\linenomath\csname old#1\endcsname}%
 {\csname oldend#1\endcsname\endlinenomath}}%
\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
 \patchAmsMathEnvironmentForLineno{#1}%
 \patchAmsMathEnvironmentForLineno{#1*}}%

\AtBeginDocument{%
 \patchBothAmsMathEnvironmentsForLineno{equation}%
 \patchBothAmsMathEnvironmentsForLineno{align}%
 \patchBothAmsMathEnvironmentsForLineno{flalign}%
 \patchBothAmsMathEnvironmentsForLineno{alignat}%
 \patchBothAmsMathEnvironmentsForLineno{gather}%
 \patchBothAmsMathEnvironmentsForLineno{multline}%
}

% control floats
\renewcommand\floatpagefraction{.9}
\renewcommand\topfraction{.9}
\renewcommand\bottomfraction{.9}
\renewcommand\textfraction{.1}
\setcounter{totalnumber}{50}
\setcounter{topnumber}{50}
\setcounter{bottomnumber}{50}

\newcommand{\jy}[1]{\textcolor{blue}{JY: #1}}
\newcommand{\eds}[1]{\textcolor{red}{EDS: (#1)}}

% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{0}

%\title{On Misuses of the Kolmogorov--Smirnov Test for One-Sample Goodness-of-Fit}
%
%\author{Anthony Zeimbekakis\\
%%   \href{mailto:anthony.zeimbekakis@uconn.edu}
%% {\nolinkurl{anthony.zeimbekakis@uconn.edu}}\\
  %Elizabeth D.  Schifano\\
  %Jun Yan\\[1ex]
  %Department of Statistics, University of Connecticut\\
%}
%\date{}

\begin{document}
%\maketitle

\if0\blind
{
  \title{\bf Project Proposal}
  \author{Zoe Macris}
\date{October 2023}
  \maketitle}

%\doublespace

\section{Introduction}
\label{sec:intro}

The topic for my paper will be a meta-analysis of research into variables that affect cycling as an individual’s mode of transport. This is impactful as biking is a more environmentally friendly alternative to transportation than cars, so factors that can increase the likelihood of biking are very important to evaluate. Cycling improvements can be anything from better bike lanes, improved social attitude to cycling, and road safety. There is a diverse array of research on this topic already, but often they focus on one distinct geographic location, like this study from New Orleans \cite{Parker2013}, on the impact of a new bike lane in the city. There is also diversity in whether a study focuses on one variable like protected bike lanes \cite{Karpinski2021}, or many covariates like in research on college campuses in the Baltimore Metropolitan Area \cite{Kelarestaghi2019}. Therefore, it is a topic of interest to investigate how the different ways of studying this issue can impact the results. Cycling is a mode of transport that is often under served infrastructure wise, so it is important to look into which improvements will serve it best, and furthermore what the body of research says and which method is most effective.

\section{Specific Aims}
\label{sec:fitted}

The research question I am hoping to address is how different types of statistics analysis and research into improving cycling conditions compare to each other. From there, we can more confidently state what improvements need to be made to encourage and facilitate cycling. This meta-analyses will be used as knowledge accumulation for the field, and also to "identify important moderators where the results of different primary studies differ from each other" \citep{Hansen2022}.

\section{Data and Methods}
\label{sec:dependence}

My data set will be a group of the studies that exist on the topic of cycling infrastructure improvements in online databases. I will chose from the databases that we are able to access through our UConn accounts, most likely Science Direct and JSTOR. With these, I will attempt to gather at least 20 studies, from doing a keyword search for “cycling infrastructure improvements” in at least these 2 databases to prevent bias.

The overall method will then be to decide inclusion criteria to determine which studies to include in my data set, and to try and ensure that there is a proportion of non-published and less cited articles in my data to combat the “Matthew Effect” where highly cited articles are found faster than less cited ones \cite{Hansen2022}. I will then use an effect size measure of z-transformed correlation coefficients, so that I am able to compare the articles. Then there will be a Qualitative meta-analysis conducted as most of the research I have observed has been qualitative surveys and case studies, so this method will help when investigating my particular research question of how the current research compares to each other. The software I will use will be R, and the package of {\em metafor} as it includes all the necessary functions for meta-analysis \cite{Hansen2022}.

\section{Discussion}
\label{sec:fittedwithdependence}

I expect to find that the research that brings in multiple covariates and diverse locations will perform the best, as the multiple correlation coefficients being examined improves the validity of research in finding the best causal variables. It might also become evident that there are holes in the current research methods, like not including land use types and density as variables, or focusing on survey style research instead of more quantitative methods. By synthesizing the research and coming to a conclusion on the most effective research, there could be also be the potential for a standardized practice for looking at cycling issues at a local level and determining what interventions are needed. If the results of this intervention are not what I expected, then that would also be useful in determining what how the field of research should pivot and which methods to focus on in the future if not the obvious path.

\section{Conclusion}
\label{sec:conclusion}

To conclude, my project will be to consolidate and analyze the existing research on structural and social improvements for cycling. This is a fairly niche topic, but I do believe in its importance. By bringing together all of this valuable research, and assessing different strategies for assessing improvement strategies, there would be potential advancements discovered for the practical implementation of infrastructure and social changes for cycling.

\bibliography{Citations}

\end{document}
%%% LocalWords: nonparametric semiparametric autocorrelation ARMA
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% ispell-personal-dictionary: ".aspell.en.pws"
%%% fill-column: 80
%%% eval: (auto-fill-mode 1)
%%% End:

### 2023-10-27 Manuscript/Manuscript.tex
Added formatting for manuscript draft

--- 2023-10-18 Proposal/ProjectProposal.tex
@@
 {
-  \title{\bf Project Proposal}
+  \title{\bf Manuscript Draft}
   \author{Zoe Macris}
-\date{October 2023}
+\date{December 2023}
   \maketitle}
@@
 
+\section{Abstract}
+\label{sec:abstract}
+
+\section{Keywords}
+\label{sec:keywords}
+
 \section{Introduction}
@@
 
-The topic for my paper will be a meta-analysis of research into variables that affect cycling as an individual’s mode of transport.
-This is impactful as biking is a more environmentally friendly alternative to transportation than cars, so factors that can increase the likelihood of biking are very important to evaluate.
-Cycling improvements can be anything from better bike lanes, improved social attitude to cycling, and road safety.
-There is a diverse array of research on this topic already, but often they focus on one distinct geographic location, like this study from New Orleans \cite{Parker2013}, on the impact of a new bike lane in the city.
-There is also diversity in whether a study focuses on one variable like protected bike lanes \cite{Karpinski2021}, or many covariates like in research on college campuses in the Baltimore Metropolitan Area \cite{Kelarestaghi2019}.
-Therefore, it is a topic of interest to investigate how the different ways of studying this issue can impact the results.
-Cycling is a mode of transport that is often under served infrastructure wise, so it is important to look into which improvements will serve it best, and furthermore what the body of research says and which method is most effective.
+\section{Data}
+\label{sec:data}
 
-\section{Specific Aims}
-\label{sec:fitted}
+\section{Methods}
+\label{sec:methods}
 
-The research question I am hoping to address is how different types of statistics analysis and research into improving cycling conditions compare to each other.
-From there, we can more confidently state what improvements need to be made to encourage and facilitate cycling.
-This meta-analyses will be used as knowledge accumulation for the field, and also to "identify important moderators where the results of different primary studies differ from each other" \citep{Hansen2022}.
+\section{Simulation}
+\label{sec:somulation}
 
-\section{Data and Methods}
-\label{sec:dependence}
+\section{Application}
+\label{sec:application}
 
-My data set will be a group of the studies that exist on the topic of cycling infrastructure improvements in online databases.
-I will chose from the databases that we are able to access through our UConn accounts, most likely Science Direct and JSTOR.
-With these, I will attempt to gather at least 20 studies, from doing a keyword search for “cycling infrastructure improvements” in at least these 2 databases to prevent bias.
+\section{Discussion and Conclusion}
+\label{sec:discandconclus}
 
-The overall method will then be to decide inclusion criteria to determine which studies to include in my data set, and to try and ensure that there is a proportion of non-published and less cited articles in my data to combat the “Matthew Effect” where highly cited articles are found faster than less cited ones \cite{Hansen2022}.
-I will then use an effect size measure of z-transformed correlation coefficients, so that I am able to compare the articles.
-Then there will be a Qualitative meta-analysis conducted as most of the research I have observed has been qualitative surveys and case studies, so this method will help when investigating my particular research question of how the current research compares to each other.
-The software I will use will be R, and the package of {\em metafor} as it includes all the necessary functions for meta-analysis \cite{Hansen2022}.
+\section{Appendix}
+\label{sec:appendix}
 
-\section{Discussion}
-\label{sec:fittedwithdependence}
+\section{Acknowledgements}
+\label{sec:acknow}
 
-I expect to find that the research that brings in multiple covariates and diverse locations will perform the best, as the multiple correlation coefficients being examined improves the validity of research in finding the best causal variables.
-It might also become evident that there are holes in the current research methods, like not including land use types and density as variables, or focusing on survey style research instead of more quantitative methods.
-By synthesizing the research and coming to a conclusion on the most effective research, there could be also be the potential for a standardized practice for looking at cycling issues at a local level and determining what interventions are needed.
-If the results of this intervention are not what I expected, then that would also be useful in determining what how the field of research should pivot and which methods to focus on in the future if not the obvious path.
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-To conclude, my project will be to consolidate and analyze the existing research on structural and social improvements for cycling.
-This is a fairly niche topic, but I do believe in its importance.
-By bringing together all of this valuable research, and assessing different strategies for assessing improvement strategies, there would be potential advancements discovered for the practical implementation of infrastructure and social changes for cycling.
+\section{Appendix}
+\label{sec:appendix}
 

### 2023-10-30 Manuscript/Manuscript.tex
cleaned up notes in draft
intro paragraph started

@@
 \linenumbers*[1]
-% %% patches to make lineno work better with amsmath
+
 \newcommand*\patchAmsMathEnvironmentForLineno[1]{%
@@
 
-%\title{On Misuses of the Kolmogorov--Smirnov Test for One-Sample Goodness-of-Fit}
-%
-%\author{Anthony Zeimbekakis\\
-%%   \href{mailto:anthony.zeimbekakis@uconn.edu}
-%% {\nolinkurl{anthony.zeimbekakis@uconn.edu}}\\
-  %Elizabeth D.  Schifano\\
-  %Jun Yan\\[1ex]
-  %Department of Statistics, University of Connecticut\\
-%}
-%\date{}
-
 \begin{document}
-%\maketitle
 
@@
 \label{sec:intro}
+
+For being around for just over 200 years, the bicycle has constantly evolved in it's utility to us as a society.
+Originally just for hobbyists, and inhibitively expensive, they are now one of the most accessible modes of transport.
+It is an excellent for of exercises for our increasingly sedentary society, giving a cardio workout that improves flexibility and isn't hard on the joints.
+It also can help people's mental health as well as physical.
+Beyond these individual benefits, cycling has a benefit for the environment and society as a whole It is a sustainable mode of transportation, not releasing any carbon emissions and requiring much less infrastructure and parking than automobiles.
+It is because of these benefits, that investing time and resources into cycling infrastructure is important.
+Bike lanes, separated paths and bike-friendly intersections can all be used to encourage cycling, leading to the benefits of improved public health and air quality, as well as making it a safe activity for those who chose to cycle.
+Additionally, cycling is only a viable option for some individuals with disabilities or limited mobility when there is proper cycling infrastructure.
+This is where statistics comes in.
+In order to reap these benefits of cycling, we can analyse data to promote cycling infrastructure to decision makers.
 
@@
 
-\section{Appendix}
-\label{sec:appendix}
-
 \bibliography{Citations}

### 2023-10-30 Manuscript/Manuscript.tex
fixed citation format
added citation to intro
eddited formatting

@@
 \linenumbers*[1]
-
+% %% patches to make lineno work better with amsmath
 \newcommand*\patchAmsMathEnvironmentForLineno[1]{%
@@
 
+\setlength{\linewidth}{5in}
+
 \begin{document}
+%\maketitle
 
@@
   \title{\bf Manuscript Draft}
-  \author{Zoe Macris}
+  \author{Zoe Macris\\
+  University of Connecticut Department of Statistics
 \date{December 2023}
@@
 For being around for just over 200 years, the bicycle has constantly evolved in it's utility to us as a society.
-Originally just for hobbyists, and inhibitively expensive, they are now one of the most accessible modes of transport.
+Originally just for hobbyists, and inhibitively expensive, they are now one of the most accessible modes of transport \cite{BIKE2023}.
 It is an excellent for of exercises for our increasingly sedentary society, giving a cardio workout that improves flexibility and isn't hard on the joints.
@@
 \label{sec:data}
-
 \section{Methods}
@@
 
-\bibliography{Citations}
+\section{Appendix}
+\label{sec:appendix}
+
+\bibliography{FinalCitations}
 

### 2023-11-07 Manuscript/Manuscript.tex
Added table to manuscript

@@
 \usepackage{lipsum}
+\usepackage{siunitx}
 \usepackage[square,numbers]{natbib}
@@
 
-\setlength{\linewidth}{5in}
+\setlength{\linewidth}{3in}
 
@@
   \title{\bf Manuscript Draft}
-  \author{Zoe Macris\\
-  University of Connecticut Department of Statistics
+  \author{Zoe Macris}
 \date{December 2023}
@@
 \label{sec:data}
+
 \section{Methods}
 \label{sec:methods}
-
-\section{Simulation}
-\label{sec:somulation}
 
@@
 \label{sec:discandconclus}
+
+The paper by Mateo-Babiano takes the approach of using by Spearman correlation to analyse the effects of various cycling measures on usage, as can be seen in ~\ref{fig:Mateo-Babiano}
+
+\begin{table}[tbp]
+\label{fig:Mateo-Babiano}
+\centering
+\caption{Length of bikeway by bikeway type in Brisbane and CityCycle areas. Spearman correlation of station usage and infrastructure type: from Mateo-Babiano paper}
+\begin{tabular}{l*{5}{p{2cm}}}
+\toprule
+{Infrastructure type} & {Length Brisbane Area (km)} & {Lenth in CityCycle area (km)} & {Correlation coefficent} & {P-value}\\
+\midrule
+Shared Pathway & 327.9 & 18.0 & 0.42 & <0.01 \\
+Bicycle Lane & 186.7 & 21.3 & 0.03 & 0.69 \\
+Bicycle Awareness Zone (BAZ) & 303.7 & 40.3 & -0.07 & 0.39 \\
+Bicycle Path & 23.9 & 2.6 & 0.27 & <0.01 \\
+Bicycle Route (BAZ) & 76.9 & 8.2 & 0.13 & 0.11 \\
+Connect & 19.5 & 5.0 & 0.16 & 0.049 \\
+Informal Off Road & 65.8 & 4.6 & 0.00 & 0.98 \\
+Informal On Road & 18.2 & 4.1 & -0.13 & 0.12 \\
+Separated Pathway & 1.8 & 1.3 & 0.29 & <0.0 \\
+\bottomrule
+\end{tabular}
+\end{table}
 
@@
 
-\bibliography{FinalCitations}
+\bibliography{Citations}
 

### 2023-11-10 Manuscript/Manuscript.tex
Added background section and edited intro and formatting

@@
 {
-  \title{\bf Manuscript Draft}
+  \title{\bf A Concise Survey on Statistical Analysis in Bike Lane Research}
   \author{Zoe Macris}
@@
 
-For being around for just over 200 years, the bicycle has constantly evolved in it's utility to us as a society.
+Given that they have been around for just over 200 years, the bicycle has  evolved considerably in it's utility to us as a society.
 Originally just for hobbyists, and inhibitively expensive, they are now one of the most accessible modes of transport \cite{BIKE2023}.
-It is an excellent for of exercises for our increasingly sedentary society, giving a cardio workout that improves flexibility and isn't hard on the joints.
-It also can help people's mental health as well as physical.
-Beyond these individual benefits, cycling has a benefit for the environment and society as a whole It is a sustainable mode of transportation, not releasing any carbon emissions and requiring much less infrastructure and parking than automobiles.
-It is because of these benefits, that investing time and resources into cycling infrastructure is important.
-Bike lanes, separated paths and bike-friendly intersections can all be used to encourage cycling, leading to the benefits of improved public health and air quality, as well as making it a safe activity for those who chose to cycle.
-Additionally, cycling is only a viable option for some individuals with disabilities or limited mobility when there is proper cycling infrastructure.
-This is where statistics comes in.
-In order to reap these benefits of cycling, we can analyse data to promote cycling infrastructure to decision makers.
+The World Health Organizations recommendation is a minimum of 150 minutes of moderate aerobic activity per week (WHO, 2021).
+This is difficult to achieve in our sedentary society, but cycling is an excellent form of exercise that can also double as the mode of transport for commuting and completing daily tasks.
+Furthermore, getting the appropriate amount of exercise can have an estimated risk reduction of 30\% for all-cause mortality, including from cardiovascular disease, coronary heart disease, stroke, diabetes and cancer.
+(Gotschi, 2014).
+It also can help people's mental health as well as physical, some studies have even demonstrated a decrease in depression symptoms from cycling for transportation (NIH, 2021).
+Beyond these individual benefits, cycling has a benefit for the environment and society as a whole.
+Transportation is a large source of greenhouse gas emissions for many countries (NIH, 2021).
+In recent years, there has been even more emphasis on sustainable and environmentally conscious transportation options in urban areas.
+Cycling fits the these criteria and has risen to prominence as a viable sustainable mode of transportation.
+It is a form of active transportation, which is defined as human powered, and thus does not release greenhouse gas emissions.
+Bikes also take up considerable less space and require significantly less infrastructure than cars as an added benefit.
+In order to promote cycling and make use of the benefits of alleviating traffic congestion, reduced emissions, and enhancing public health, it has become necessary to plan and evaluate cycling infrastructure, and bike lanes more specifically.
+Statistical research and analysis on bike lanes provides crucial insights into the usage patterns, attitudes, commute rates, bicycle traffic and safety.
+This survey paper aims to provide an comprehensive examination of the existing body of statistical research into bike lines.
+With this, we hope to show trends in the research, give an overview of statistical findings and identify areas that can be further developed.
+
+\section{Background}
+\label{sec:Background}
 
@@
 \begin{table}[tbp]
+\small
 \label{fig:Mateo-Babiano}
@@
 \caption{Length of bikeway by bikeway type in Brisbane and CityCycle areas. Spearman correlation of station usage and infrastructure type: from Mateo-Babiano paper}
-\begin{tabular}{l*{5}{p{2cm}}}
+\begin{tabular}{l*{5}{p{1.5cm}}}
 \toprule

### 2023-11-10 Manuscript/Manuscript.tex
Fixed it and actually added background section and edited intro and formatting

@@
 Originally just for hobbyists, and inhibitively expensive, they are now one of the most accessible modes of transport \cite{BIKE2023}.
-The World Health Organizations recommendation is a minimum of 150 minutes of moderate aerobic activity per week (WHO, 2021).
+The World Health Organizations recommendation is a minimum of 150 minutes of moderate aerobic activity per week \citep{WHO2020}.
 This is difficult to achieve in our sedentary society, but cycling is an excellent form of exercise that can also double as the mode of transport for commuting and completing daily tasks.
-Furthermore, getting the appropriate amount of exercise can have an estimated risk reduction of 30\% for all-cause mortality, including from cardiovascular disease, coronary heart disease, stroke, diabetes and cancer.
-(Gotschi, 2014).
-It also can help people's mental health as well as physical, some studies have even demonstrated a decrease in depression symptoms from cycling for transportation (NIH, 2021).
-Beyond these individual benefits, cycling has a benefit for the environment and society as a whole.
-Transportation is a large source of greenhouse gas emissions for many countries (NIH, 2021).
-In recent years, there has been even more emphasis on sustainable and environmentally conscious transportation options in urban areas.
-Cycling fits the these criteria and has risen to prominence as a viable sustainable mode of transportation.
-It is a form of active transportation, which is defined as human powered, and thus does not release greenhouse gas emissions.
-Bikes also take up considerable less space and require significantly less infrastructure than cars as an added benefit.
-In order to promote cycling and make use of the benefits of alleviating traffic congestion, reduced emissions, and enhancing public health, it has become necessary to plan and evaluate cycling infrastructure, and bike lanes more specifically.
+\par
 Statistical research and analysis on bike lanes provides crucial insights into the usage patterns, attitudes, commute rates, bicycle traffic and safety.
@@
 With this, we hope to show trends in the research, give an overview of statistical findings and identify areas that can be further developed.
+\par
+The rest of the paper will be organized in the following manner.
+Section \ref{sec:Background} will present a background about bike lanes and why they are important.
+Section \ref{sec:methodanddata} will present how the survey was conducted.
+Section \ref{sec:disc} will discuss the findings and recommendations.
+Then \ref{sec:conc} will conclude the paper.
 
@@
 
-\section{Data}
-\label{sec:data}
+Furthermore, according to \citet{Gtschi2015}, getting the appropriate amount of exercise has an estimated risk reduction of 30\% for all-cause mortality, including from cardiovascular disease, coronary heart disease, stroke, diabetes and cancer .
+It also can help people's mental health as well as physical, some studies have even demonstrated a decrease in depression symptoms from cycling for transportation \cite{Green2021}.
+\par
+Beyond these individual benefits, cycling has a benefit for the environment and society as a whole.
+Transportation is a large source of greenhouse gas emissions for many countries \cite{Green2021}.
+In recent years, there has been even more emphasis on sustainable and environmentally conscious transportation options in urban areas.
+Cycling fits the these criteria and has risen to prominence as a viable sustainable mode of transportation.
+It is a form of active transportation, which is defined as human powered, and thus does not release greenhouse gas emissions.
+Bikes also take up considerable less space and require significantly less infrastructure than cars as an added benefit.\par
+In order to promote cycling and make use of the benefits of alleviating traffic congestion, reduced emissions, and enhancing public health, it is  necessary to plan and evaluate cycling infrastructure, and bike lanes more specifically.
 
-\section{Methods}
-\label{sec:methods}
+\section{Method and Data}
+\label{sec:methodanddata}
 
-\section{Application}
-\label{sec:application}
-
-\section{Discussion and Conclusion}
-\label{sec:discandconclus}
+\section{Discussion}
+\label{sec:disc}
 
@@
 
+\section{Conclusion}
+\label{sec:conc}
+
 \section{Appendix}

### 2023-11-10 Manuscript/Manuscript.tex
added figure and beginnings of results

@@
 \linenumbers*[1]
-% %% patches to make lineno work better with amsmath
-\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
- \expandafter\let\csname old#1\expandafter\endcsname\csname #1\endcsname
- \expandafter\let\csname oldend#1\expandafter\endcsname\csname end#1\endcsname
- \renewenvironment{#1}%
- {\linenomath\csname old#1\endcsname}%
- {\csname oldend#1\endcsname\endlinenomath}}%
-\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
- \patchAmsMathEnvironmentForLineno{#1}%
- \patchAmsMathEnvironmentForLineno{#1*}}%
-
-\AtBeginDocument{%
- \patchBothAmsMathEnvironmentsForLineno{equation}%
- \patchBothAmsMathEnvironmentsForLineno{align}%
- \patchBothAmsMathEnvironmentsForLineno{flalign}%
- \patchBothAmsMathEnvironmentsForLineno{alignat}%
- \patchBothAmsMathEnvironmentsForLineno{gather}%
- \patchBothAmsMathEnvironmentsForLineno{multline}%
-}
 
@@
   \title{\bf A Concise Survey on Statistical Analysis in Bike Lane Research}
-  \author{Zoe Macris}
+  \author{Zoe Macris\\
+  University of Connecticut}
 \date{December 2023}
@@
 
-Furthermore, according to \citet{Gtschi2015}, getting the appropriate amount of exercise has an estimated risk reduction of 30\% for all-cause mortality, including from cardiovascular disease, coronary heart disease, stroke, diabetes and cancer .
+\subsection{Benefits of Cycling}
+\label{sec:benefit}
+
+According to \citet{Gtschi2015}, getting the appropriate amount of exercise has an estimated risk reduction of 30\% for all-cause mortality, including from cardiovascular disease, coronary heart disease, stroke, diabetes and cancer .
 It also can help people's mental health as well as physical, some studies have even demonstrated a decrease in depression symptoms from cycling for transportation \cite{Green2021}.
@@
 In order to promote cycling and make use of the benefits of alleviating traffic congestion, reduced emissions, and enhancing public health, it is necessary to plan and evaluate cycling infrastructure, and bike lanes more specifically.
+Statistical analysis can come into play here and help prove whether bike lanes make a significant impact on the propensity of people cycling and their safety while doing it.
+
+\subsection{Types of Infrastructure}
+\label{sec:bikeshare}
+
+The Connecticut State government describes the common facility types used to accommodate cyclists as Shared Roadways, Wide Curb-lanes, Bicycle Lanes and Multi-use Paths.
 
@@
 
+\section{Results}
+\label{sec:results}
+
+\subsection{Correlation and Regression Analysis}
+\label{sec:corr}
+
+2, 4, 5 Binary Probit Regression Analysis.
+
+\subsection{Multiple Level Logistic Regression}
+\label{sec:mult}
+
+3.
+The paper from \citet{3Teixeira2020} uses Multipple Level Logistic Regression to analyze the impact of cycling in various cities with different cycling infrastructure on stress markers.
+This analysis resulted in the data shown in Table ~\ref{fig:stress}.
+\begin{figure}[tbp]
+    \centering
+    \includegraphics[width=0.5\textwidth]{stresstable2.jpeg}
+    \caption{Distribution of Stress by City from Teixeira Study}
+    \label{fig:stress}
+\end{figure}
+
+\subsection{Generalized Linear Model}
+\label{sec:gen}
+
 \section{Discussion}
@@
 
-The paper by Mateo-Babiano takes the approach of using by Spearman correlation to analyse the effects of various cycling measures on usage, as can be seen in ~\ref{fig:Mateo-Babiano}
+The paper by Mateo-Babiano takes the approach of using by Spearman correlation to analyse the effects of various cycling measures on usage, as can be seen in ~\ref{table:MB}
 
@@
 \small
-\label{fig:Mateo-Babiano}
+\label{table:MB}
 \centering

### 2023-11-11 Manuscript/Manuscript.tex
added more to background section

@@
 
+In order to understand the research into bike lanes, these topics should be understood.
+
 \subsection{Benefits of Cycling}
@@
 
-The Connecticut State government describes the common facility types used to accommodate cyclists as Shared Roadways, Wide Curb-lanes, Bicycle Lanes and Multi-use Paths.
+The Connecticut State government describes the common facility types used to accommodate cyclists as Shared Roadways, Wide Curb-lanes, Bicycle Lanes and Multi-use Paths.\par
+Shared roadways are where bicycle and automobile travel are allowed, all streets and roads other than controlled highways, are in this category.
+They do not provide any added protection to cyclists, but a street's designation as shared roadway indicates to cyclists that there are advantages to using the route over alternatives.
+Wide curb lanes are still for sharing between bicycle and motorized traffic, but they provide more distance between bicyclists and vehicles and protection from high traffic speeds.
+They are created by widening roadways or narrowing traffic lanes, or both.\par
+The category of bicycle lanes is defined as painted and signed lanes on the shoulder of streets, to improve conditions for bicyclists and to protect them from traffic volume and speed.
+Being designated as a bike lane street, means that more "pavements surface improvements, stronger sweeping programs, special signal facilities, etc" occur on them to increase safety and comfort for cyclists.
+\par
+The last level of cycling infrastructure is multi-use paths, on which cyclists have exclusive rights-of-way and don't cross The flow of automobiles more than necessary.
+These can be both recreational opportunities or high=speed commuter routes for cyclists.
+\par
+The research in this survey focuses on the infrastructure of bicycle lanes, and whether they are sufficient to increase the propensities of people to cycle, and their safety while they are cycling.
 

### 2023-11-11 Manuscript/Manuscript.tex
added citations to background

@@
 \linenumbers*[1]
-
-% control floats
-\renewcommand\floatpagefraction{.9}
-\renewcommand\topfraction{.9}
-\renewcommand\bottomfraction{.9}
-\renewcommand\textfraction{.1}
-\setcounter{totalnumber}{50}
-\setcounter{topnumber}{50}
-\setcounter{bottomnumber}{50}
-
-\newcommand{\jy}[1]{\textcolor{blue}{JY: #1}}
-\newcommand{\eds}[1]{\textcolor{red}{EDS: (#1)}}
 
@@
 Shared roadways are where bicycle and automobile travel are allowed, all streets and roads other than controlled highways, are in this category.
-They do not provide any added protection to cyclists, but a street's designation as shared roadway indicates to cyclists that there are advantages to using the route over alternatives.
+They do not provide any added protection to cyclists, but a street's designation as shared roadway indicates to cyclists that there are advantages to using the route over alternatives \cite{CTDOT2023}.
+\par
 Wide curb lanes are still for sharing between bicycle and motorized traffic, but they provide more distance between bicyclists and vehicles and protection from high traffic speeds.
-They are created by widening roadways or narrowing traffic lanes, or both.\par
+They are created by widening roadways or narrowing traffic lanes, or both \cite{CTDOT2023}.\par
 The category of bicycle lanes is defined as painted and signed lanes on the shoulder of streets, to improve conditions for bicyclists and to protect them from traffic volume and speed.
-Being designated as a bike lane street, means that more "pavements surface improvements, stronger sweeping programs, special signal facilities, etc" occur on them to increase safety and comfort for cyclists.
+Being designated as a bike lane street, means that more "pavements surface improvements, stronger sweeping programs, special signal facilities, etc" occur on them to increase safety and comfort for cyclists \cite{CTDOT2023}.
 \par
 The last level of cycling infrastructure is multi-use paths, on which cyclists have exclusive rights-of-way and don't cross The flow of automobiles more than necessary.
-These can be both recreational opportunities or high=speed commuter routes for cyclists.
+These can be both recreational opportunities or high=speed commuter routes for cyclists \cite{CTDOT2023}.
 \par

### 2023-11-11 Manuscript/Manuscript.tex
worked on methods section and identfying results

@@
 
+To conduct this comprehensive survey of statistical analyses on bike lanes, a search was conducted of academic databases such as Science Direct, ProQuest, MDPI, and PubMed.
+These searches were conducted through the University of Connecticut library of Databases to ensure they were papers that were a able to be accessed.
+Specific terms were used including "bike lane", "statistical analysis", and "cycling infrastructure" in order to identify relevant papers.
+The date range for literature was defined as 2012 to the present, upon evaluation of typical date range of the available literature.
+\par
+
+\subsection{Criteria of Inclusion and Exclusion}
+\label{sec:inc}
+
+Literature was included in the survey if it met these criteria:
+
+\begin{enumerate}
+        \item Whether the paper held sufficient statistical analysis on the topic of bike lanes. 
+        \item Being publicized in a peer-reviewed, reputable journal.
+        \item Availability of paper for access using University of Connecticut student status. 
+\end{enumerate}
+
+\subsection{Data}
+\label{sec:data}
+
+The data in this survey paper is the types of statistical analyses conducted by the identified literature from method given above.
+A selection of eleven papers resulted from this, and the approach used to identify relevant data from the papers to be discussed in the survey paper was done as follows.
+The specific type of statistical analysis conducted in the paper was identified.
+Alongside the method and variables used by the researchers in the study.
+The results from the data collection are displayed in ~\ref{sec:results}.
+
 \section{Results}
@@
 
-2, 4, 5 Binary Probit Regression Analysis.
+2, 4, 5, 7 Binary Probit Regression Analysis.
 
@@
 
-3.
+3, 10.
 The paper from \citet{3Teixeira2020} uses Multipple Level Logistic Regression to analyze the impact of cycling in various cities with different cycling infrastructure on stress markers.
@@
 \label{sec:gen}
+
+\subsection{Zero-inflated Poisson regression mode}
+\label{sec:pois}
+
+paper 8, 9
 

### 2023-11-12 Manuscript/Manuscript.tex
worked on results section

@@
 
-2, 4, 5, 7 Binary Probit Regression Analysis.
-
-\subsection{Multiple Level Logistic Regression}
-\label{sec:mult}
-
-3, 10.
-The paper from \citet{3Teixeira2020} uses Multipple Level Logistic Regression to analyze the impact of cycling in various cities with different cycling infrastructure on stress markers.
-This analysis resulted in the data shown in Table ~\ref{fig:stress}.
-\begin{figure}[tbp]
-    \centering
-    \includegraphics[width=0.5\textwidth]{stresstable2.jpeg}
-    \caption{Distribution of Stress by City from Teixeira Study}
-    \label{fig:stress}
-\end{figure}
-
-\subsection{Generalized Linear Model}
-\label{sec:gen}
-
-\subsection{Zero-inflated Poisson regression mode}
-\label{sec:pois}
-
-paper 8, 9
-
-\section{Discussion}
-\label{sec:disc}
-
-The paper by Mateo-Babiano takes the approach of using by Spearman correlation to analyse the effects of various cycling measures on usage, as can be seen in ~\ref{table:MB}
+The correlation and regression analysis approach of statistical research on bicycle lanes is used to establish significant relationships amongst variables.
+In \citet{1MateoBabiano2016}, the approach using Spearman's correlation coefficient rho was used, which was suitable because the variables deviated from a normal distribution.
+The variables used were Public bicycle-sharing programs (PBSP) station usage frequency and length of bike-ways, which do not follow a normal distribution.
+The results of the Spearman correlation of station usage and infrastructure type can be seen in ~\ref{table:MB}, where shred pathways, bicycle paths, connections, and separated pathways were shown to have a significant impact on PBSP usage.
+1, 2, 7 .
 
@@
 
+\subsection{Binary Regression Models}
+\label{sec:bin}
+
+In the paper by \citet{2Yujun2019}, binary probit regression analysis was used to analyze the choice of cycling for commuting, since the dependent variable to choice to bicycle to commute has two outcomes:
+
+\begin{itemize}
+    \item 0, the individual does not commute by cycling.
+    \item 1, the individual commuted by cycling at least once per week.
+\end{itemize}
+
+For the binary model, a latent or unobserved variable y* is assumed that ranges from $\infty$ to $-\infty$, which is related to the independent variable by the equation $y^{*}_{i} = x_{i}\beta + \epsilon_{i}$.
+In the context of this survey paper, this latent variable are what underlies the decision making process of bicycle commuting.
+Where $X_{i}$ is a matrix of independent variables and $\beta$ is a vector of coefficients to be estimated and $\epsilon$ is random error \cite{LONG2001}.
+
+papers 2, 5
+
+\subsection{Multiple Level  Regression Analysis}
+\label{sec:mult}
+
+4, 10.
+The paper from \citet{3Teixeira2020} uses Multiple Level Logistic Regression to analyze the impact of cycling in various cities with different cycling infrastructure on stress markers.
+This analysis resulted in the data shown in Table ~\ref{fig:stress}.
+\begin{figure}[tbp]
+    \centering
+    \includegraphics[width=0.5\textwidth]{stresstable2.jpeg}
+    \caption{Distribution of Stress by City from Teixeira Study}
+    \label{fig:stress}
+\end{figure}
+
+Two types of models were used in \citet{4Buehler2011}, a log-log Ordinary Least Square (OLS) model "with the dependent variable being the bike commuters per 10,000 population.
+AS well as a Binary Logit Proportional model "with the share of bike commuters in each city as the dependent variable".
+This paper analyzed the role of cycling infrastructure on commutership by bike in 90 of the largest 100 U.S.
+cities.
+The OLS model is used for estimating coefficients of linear regression that describe the relationship between one or more quantitative independent variables and a dependent variable.
+With p explanatory variables, the OLS regression model is:
+\[Y = \beta_{0}+\sum_{j=1,\dots, p}{\beta_{j}X_{j}}+\epsilon\]
+
+\subsection{Zero-inflated Poisson regression mode}
+\label{sec:pois}
+
+paper 8, 9
+
+\subsection{Generalized Linear Model}
+\label{sec:gen}
+
+paper 6
+
+\section{Discussion}
+\label{sec:disc}
+
 \section{Conclusion}

### 2023-11-12 Manuscript/Manuscript.tex
added more to results section

@@
 
-papers 2, 5
+The binary logistic regression model is also used in this field of statistical research to predict the likelihood of a successful event occurring, like a high number of cycling routes close to green areas \cite{5CamposSnchez2019}.
+In order to conduct this model, all the variables had to be recoded to dichotomous categorical variables (1-0).
+For example, bicycle racks where 1=bicycle racks in buffer area, 0= no bicycle racks.
 
@@
 
-4, 10.
 The paper from \citet{3Teixeira2020} uses Multiple Level Logistic Regression to analyze the impact of cycling in various cities with different cycling infrastructure on stress markers.
@@
 Two types of models were used in \citet{4Buehler2011}, a log-log Ordinary Least Square (OLS) model "with the dependent variable being the bike commuters per 10,000 population.
-AS well as a Binary Logit Proportional model "with the share of bike commuters in each city as the dependent variable".
+As well as a Binary Logit Proportional model "with the share of bike commuters in each city as the dependent variable".
 This paper analyzed the role of cycling infrastructure on commutership by bike in 90 of the largest 100 U.S.
 cities.
-The OLS model is used for estimating coefficients of linear regression that describe the relationship between one or more quantitative independent variables and a dependent variable.
+The OLS model is used for estimating coefficients of linear regression that describe the relationship between one or more quantitative independent variables and a dependent variable \cite{XLSTAT2023}.
 With p explanatory variables, the OLS regression model is:
@@
 
-\subsection{Zero-inflated Poisson regression mode}
+In the group of papers selected, the multinomial logit (MNL) model was used to estimate the travel choice of bicycle for commuting \cite{10Zhao2013}.
+
+\subsection{Zero-inflated Poisson Regression Mode}
 \label{sec:pois}
 
-paper 8, 9
+A different approach that was used in the research into bike lanes was to use a zero-inflated Poisson regression model to estimate the change in cycle-motor vehicle collisions \cite{8Bhatia2016}.
+This model is used since the design is looking at collision rates pre to post instillation of bike lanes, and since the model allows for an over-abundance of zero counts in the data.
+The Poisson distribution's p.m.f is:
+\[P(Y=y) = \exp{(-\lambda)\lambda^{y}}/y!\]
+
+The Poisson model is also used in \citet{9Cantisani2021} to "address the randomness due to the perception and decision of road users at the intersections", as their research is specifically on the crash likelihood of cyclists at roundabouts with different infrastructure types.
 
@@
 
-paper 6
+The final method identified from the surveyed papers was to use the generalized linear model to predict the vehicle delays caused by bicycle traffic versus other variables.
+Alongside this method, the cumulative curve method as used to extract traffic flow data from videos \cite{6Pu2017}.
+The basic model of the generalized linear model is:
+\[Y_{nx1} = X_{nxp}\beta_{px1}+\epsilon_{nx1}\]
+Where the matrix of observed values of dependent variables is  $Y_{nx1}$, $X_{nxp}$ is the matrix of observed explanatory variables, $\beta_{px1} =$ is the matrix of coefficients for explanatory variables, and $\epsilon_{nx1}$ is the error.
+Using this model is reported to help to understand how each factor contributed to the delay of cyclists on urban streets.
 

### 2023-11-12 Manuscript/Manuscript.tex
worked on results section

@@
 
+\providecommand{\keywords}[1]
+{
+  \small	
+  \textbf{\textit{Keywords---}} #1
+}
+
 \begin{document}
@@
 
-\section{Abstract}
+\begin{abstract}
+This survey paper examines the evolving field of statistical analysis of bicycle lanes.
+Cycling has an evolving role in society, and has taken a place as a sustainable and accessible mode of transportation and exercise.
+In order for cycling to be accessible for the most number of people, investments into bike lanes and cycling infrastructure have to be made.
+Through an examination of existing studies, we explore the current trends in method to show whether bike lanes have a statistically significant effect on cycling outcomes.
+\end{abstract}
 \label{sec:abstract}
 
-\section{Keywords}
-\label{sec:keywords}
+\keywords{Bike Lanes, Regression Analysis, Binary Regression Models, Multiple Level Regression Analysis, Zero-Inflated Poisson, Generalized Linear Model}
 
@@
 Using this model is reported to help to understand how each factor contributed to the delay of cyclists on urban streets.
+\begin{figure}[tbp]
+    \centering \includegraphics[width=1\textwidth]{BikeTrafficResults.png}
+    \caption{Results table from Research on Bicycle Traffic from Pu et al.}
+    \label{fig:traffic}
+\end{figure}
 

### 2023-11-12 Manuscript/Manuscript.tex
added citation in Poisson section

@@
 A different approach that was used in the research into bike lanes was to use a zero-inflated Poisson regression model to estimate the change in cycle-motor vehicle collisions \cite{8Bhatia2016}.
-This model is used since the design is looking at collision rates pre to post instillation of bike lanes, and since the model allows for an over-abundance of zero counts in the data.
+This model is used since the design is looking at collision rates pre to post instillation of bike lanes, and since the model allows for an over-abundance of zero counts in the data \cite{Giles2010}.
 The Poisson distribution's p.m.f is:

### 2023-11-13 Manuscript/Manuscript.tex
added discussion section

@@
 
+The findings from this survey paper show the multifaceted approaches being taken in the field of research into cycling infrastructure, and how important they are to encourage sustainable urban transportation.
+In this discussion section will include; key themes, criticisms, and potential future pathways for similar research.
+\par
+
+The different types of cycling infrastructure, especially bike lanes, are shown in this body of research to have a significant impact on increasing cycling ridership.
+Whether it's an increase in bike-shares or commutership, this relationship is shown in the papers.
+This is essential when it comes to appealing to policy makers and decision makers in communities to convince them to add cycling infrastructure to their area.
+Statistical analyses are influential in providing actionable insights, including the correlation between infrastructure types existing in an area and increased cycling.
+\par
+
+Studies like \citet{1MateoBabiano2016} show how effective simple methods like Spearman's correlation coefficient can be at revealing the impact of bike lanes on PBSP usage.
+These sorts of results can lead to insights for urban planners when it comes to designing cities.
+\par
+
+Predictive models were also used, like binary regression models in \citet{2Yujun2019} to provide insight into all the factors influencing an individuals' choice to cycle for commuting.
+These predictive models offer ways for policy makers to encourage cycling as a successful commuting option in their cities.\par
+
+Some future directions this field could go include focusing on more that just high socioeconomic areas.
+This type of research has only really been done in affluent countries, likely because a lot of the research has been based off of bike-share systems.
+Which leads into another point of improvements, where there could be better ways of collecting data on cyclists, as they are often excluding people who own their own bikes from the data.
+Additionally, there is room for more cost-benefit analyses on the economic impact of investing in cycling infrastructure.
+When you create such infrastructure, there could be less congestion and damage to the automobile infrastructure.
+Which would be beneficial to persuading policy makers towards creating more bike lanes and encouraging cycling.
+
 \section{Conclusion}

### 2023-11-13 Manuscript/Manuscript.tex
added conclusion

@@
 
+In conclusion, this survey of statistical research on bike lanes offers a current snapshot of frequently used methods in the analysis of bike lanes.
+The significance of bike lanes in increasing cycling highlights the need for continued research and innovative statistical analysis to understand how to overcome the challenges of congestion, safety, and sustainability in transportation.
+This supports the efforts of enhancing cycling infrastructure for the benefits of individuals experiences while cycling and the betterment of entire communities.
+
 \section{Appendix}

### 2023-11-13 Manuscript/Manuscript.tex
added to results section

@@
 This survey paper examines the evolving field of statistical analysis of bicycle lanes.
-Cycling has an evolving role in society, and has taken a place as a sustainable and accessible mode of transportation and exercise.
+Cycling has an important role in society, and has taken a place as a sustainable and accessible mode of transportation and exercise.
 In order for cycling to be accessible for the most number of people, investments into bike lanes and cycling infrastructure have to be made.
@@
 The results of the Spearman correlation of station usage and infrastructure type can be seen in ~\ref{table:MB}, where shred pathways, bicycle paths, connections, and separated pathways were shown to have a significant impact on PBSP usage.
-1, 2, 7 .
+\par
+Other analyses used include Differences-in-Differences, Pearson's R correlation coefficient, Panel regressions, and Counterfactual based on control \cite{Karpinski2021}.
+These were used when the data being analyzed was usership of Boston's bike share program before and after the addition of bike lanes.
 

### 2023-12-06 Manuscript/Manuscript.tex
added acknowledgements
added to intro section
added figures and text for figures

@@
 Statistical research and analysis on bike lanes provides crucial insights into the usage patterns, attitudes, commute rates, bicycle traffic and safety.
+Other survey papers on research into bike lanes have neglected to focus on the statistical analyses used in the research \cite{7Mlenberg2019}.
 This survey paper aims to provide an comprehensive examination of the existing body of statistical research into bike lines.
@@
 
-The Connecticut State government describes the common facility types used to accommodate cyclists as Shared Roadways, Wide Curb-lanes, Bicycle Lanes and Multi-use Paths.\par
+The Connecticut State government describes the common facility types used to accommodate cyclists as Shared Roadways (Informal On Road), Wide Curb-lanes, Bicycle Lanes and Multi-use Paths.
+The visuals in Figure ~\ref{fig:bikelane}, show an even wider array of potential infrastructures.
+In the U.S., commonly seen types are Bicycle Awareness Zones, Informal On Road and Bicycle Lanes as seen in the images.
+The supposition of much of the research analyzed here is that the more advanced the infrastructure is, the more likely people are to cycle \cite{1MateoBabiano2016}.\par
+
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=0.75\textwidth]{Bikelane.jpg}
+    \caption{Bike Lane Comparison \cite{1MateoBabiano2016}}
+    \label{fig:bikelane}
+\end{figure}
+
 Shared roadways are where bicycle and automobile travel are allowed, all streets and roads other than controlled highways, are in this category.
@@
 \par
-Wide curb lanes are still for sharing between bicycle and motorized traffic, but they provide more distance between bicyclists and vehicles and protection from high traffic speeds.
+Wide curb lanes are still require sharing between bicycle and motorized traffic, but they provide more distance between bicyclists and vehicles and protection from high traffic speeds.
 They are created by widening roadways or narrowing traffic lanes, or both \cite{CTDOT2023}.\par
@@
 The final method identified from the surveyed papers was to use the generalized linear model to predict the vehicle delays caused by bicycle traffic versus other variables.
-Alongside this method, the cumulative curve method as used to extract traffic flow data from videos \cite{6Pu2017}.
-The basic model of the generalized linear model is:
+
+\begin{figure}[hbt!]
+    \centering \includegraphics[width=1\textwidth]{6973089.fig.004a.png}
+    \caption{Relationship between bicycle flow and density}
+    \label{fig:flow}
+\end{figure}
+
+Alongside this method, the cumulative curve method as used to extract traffic flow data from videos \cite{6Pu2017}. The basic model of the generalized linear model is:
 \[Y_{nx1} = X_{nxp}\beta_{px1}+\epsilon_{nx1}\]
@@
 Using this model is reported to help to understand how each factor contributed to the delay of cyclists on urban streets.
-\begin{figure}[tbp]
+\begin{figure}[hbt!]
     \centering \includegraphics[width=1\textwidth]{BikeTrafficResults.png}
@@
 
-\section{Appendix}
-\label{sec:appendix}
-
 \section{Acknowledgements}
 \label{sec:acknow}
+
+I would like to express my appreciation to Professor Jun Yan for his guidance in creating this paper.
 

### 2023-12-06 Manuscript/Manuscript.tex
added to binary regression section

@@
 
+\usepackage{setspace} \doublespacing
 \usepackage{amsmath}
@@
 The binary logistic regression model is also used in this field of statistical research to predict the likelihood of a successful event occurring, like a high number of cycling routes close to green areas \cite{5CamposSnchez2019}.
-In order to conduct this model, all the variables had to be recoded to dichotomous categorical variables (1-0).
-For example, bicycle racks where 1=bicycle racks in buffer area, 0= no bicycle racks.
+Binary logistic regression serves as an indispensable tool in predictive modeling due to its versatile applications and tailored approach to analyzing binary dependent variables.
+Unlike linear regression, which is suitable for predicting continuous values, binary logistic regression is specifically designed for situations where the outcome is dichotomous, such as survival vs.
+death, presence vs.
+absence, or default vs.
+non-default in loan scenarios.
+In the case of \citet{5CamposSnchez2019}, multiple variables are coded 1-0 in a binary fashion and can be seen in Table ~\ref{fig:vartable}.
+\par
+\begin{figure}[hbt!]
+    \centering \includegraphics[width=1\textwidth]{vartable.png}
+    \caption{Variable Table for Binary Logistic Regression Model}
+    \label{fig:vartable}
+\end{figure}
+
+One of the prime reasons for favoring binary logistic regression over linear regression for binary outcomes is the inherent nature of the dependent variable.
+In logistic regression, the model predicts the probability that the dependent variable will assume a value of 1.
+This probability is modeled using a logit function, ensuring the estimation of the relationship between independent variables and the probability of the event occurring.
+
+The logistic regression model itself relies on statistical estimation methods, primarily the maximum likelihood estimation.
+This method aids in determining the coefficients of the model, such as 'B0' to 'Bk', which correspond to the influence of each independent variable on the log odds of the binary outcome.
+These coefficients are estimated using iterative algorithms like Fisher scoring or the Newton-Raphson method, allowing for practical implementation using programming languages like R or Python \cite{Penman_2022}.
 
@@
 \begin{figure}[hbt!]
-    \centering \includegraphics[width=1\textwidth]{6973089.fig.004a.png}
+    \centering \includegraphics[width=1\textwidth]{flowdensity.png}
     \caption{Relationship between bicycle flow and density}
@@
 Using this model is reported to help to understand how each factor contributed to the delay of cyclists on urban streets.
+In Table ~\ref{fig:traffic}, the results are show of Flow vs Density.
 \begin{figure}[hbt!]

### 2023-12-14 Manuscript/Manuscript.tex
added to explanation of approached

@@
 This survey paper examines the evolving field of statistical analysis of bicycle lanes.
-Cycling has an important role in society, and has taken a place as a sustainable and accessible mode of transportation and exercise.
+Cycling plays an important role in society, and has taken a place as a sustainable and accessible mode of transportation and exercise.
 In order for cycling to be accessible for the most number of people, investments into bike lanes and cycling infrastructure have to be made.
@@
 non-default in loan scenarios.
-In the case of \citet{5CamposSnchez2019}, multiple variables are coded 1-0 in a binary fashion and can be seen in Table ~\ref{fig:vartable}.
+In the case of \citet{5CamposSnchez2019}, multiple variables are coded 1-0 in a binary fashion and can be seen in Figure ~\ref{fig:vartable}.
 \par
@@
 The paper from \citet{3Teixeira2020} uses Multiple Level Logistic Regression to analyze the impact of cycling in various cities with different cycling infrastructure on stress markers.
-This analysis resulted in the data shown in Table ~\ref{fig:stress}.
-\begin{figure}[tbp]
+This analysis resulted in the data shown in Figure ~\ref{fig:stress}, of stress levels measured in different cities.
+The results of this research found that riding on a protected bike lane significantly reduces cyclists stress levels compared to cycling on the general use street.
+\begin{figure}[hbp!]
     \centering
@@
 
-In the group of papers selected, the multinomial logit (MNL) model was used to estimate the travel choice of bicycle for commuting \cite{10Zhao2013}.
+In the group of papers addressed, the multinomial logit (MNL) model was used to estimate the travel choice of bicycle for commuting \cite{10Zhao2013}.
 
@@
 
-The final method identified from the surveyed papers was to use the generalized linear model to predict the vehicle delays caused by bicycle traffic versus other variables.
+The final method identified from the surveyed papers was to use the generalized linear model (GLM) to predict the vehicle delays caused by bicycle traffic versus other variables.
+The GLM has the benefit of being able to accommodate various types of response variables, including continuous, binary, count, and categorical data.
+It allows for different types of probability distributions such as Gaussian, Poisson, Binomial, etc., making it applicable in a wide range of scenarios.
+Additionally, GLMs are not restricted to normality assumptions, which makes them suitable for data that is distributed non-normally \cite{PennState2023}.
+
+Alongside this method, the cumulative curve method as used to extract traffic flow data from videos \cite{6Pu2017}. The basic model of the generalized linear model is:
+\[Y_{nx1} = X_{nxp}\beta_{px1}+\epsilon_{nx1}\]
+Where the matrix of observed values of dependent variables is  $Y_{nx1}$, $X_{nxp}$ is the matrix of observed explanatory variables, $\beta_{px1} =$ is the matrix of coefficients for explanatory variables, and $\epsilon_{nx1}$ is the error.
+Using this model is reported to help to understand how each factor contributed to the delay of cyclists on urban streets.
+In Figure ~\ref{fig:traffic}, the results are shown of results of the significance of multiple variables on vehicle delay, and it can be seen that with this method, bicycle and vehicle flow as well as the number of vehicle lanes, has a significant effect on vehicle delay.
+The results of flow vs.
+density are also shown in Figure ~\ref{fig:flow}, and reveals that the average bicycle speed decreases slightly as the density increases while  the flow is still increasing, and  when there is high density the variation of bicycle speed decreases a great deal.
+These results are also consistant across multople locations of urban streets.
+\begin{figure}[hbt!]
+    \centering \includegraphics[width=1\textwidth]{BikeTrafficResults.png}
+    \caption{Results table from Research on Bicycle Traffic from Pu et al.}
+    \label{fig:traffic}
+\end{figure}
 
@@
     \label{fig:flow}
-\end{figure}
-
-Alongside this method, the cumulative curve method as used to extract traffic flow data from videos \cite{6Pu2017}. The basic model of the generalized linear model is:
-\[Y_{nx1} = X_{nxp}\beta_{px1}+\epsilon_{nx1}\]
-Where the matrix of observed values of dependent variables is  $Y_{nx1}$, $X_{nxp}$ is the matrix of observed explanatory variables, $\beta_{px1} =$ is the matrix of coefficients for explanatory variables, and $\epsilon_{nx1}$ is the error.
-Using this model is reported to help to understand how each factor contributed to the delay of cyclists on urban streets.
-In Table ~\ref{fig:traffic}, the results are show of Flow vs Density.
-\begin{figure}[hbt!]
-    \centering \includegraphics[width=1\textwidth]{BikeTrafficResults.png}
-    \caption{Results table from Research on Bicycle Traffic from Pu et al.}
-    \label{fig:traffic}
 \end{figure}

### 2023-12-14 Manuscript/Manuscript.tex
added more exlplanations to each model

@@
 The variables used were Public bicycle-sharing programs (PBSP) station usage frequency and length of bike-ways, which do not follow a normal distribution.
-The results of the Spearman correlation of station usage and infrastructure type can be seen in ~\ref{table:MB}, where shred pathways, bicycle paths, connections, and separated pathways were shown to have a significant impact on PBSP usage.
+The results of the Spearman correlation of station usage and infrastructure type can be seen in Table ~\ref{table:MB}, where shared pathways, bicycle paths, connections, and separated pathways were shown to have a significant impact on PBSP usage.
 \par
@@
 \end{table}
+
+While a fairly simple technique, basic regression and correlation analyses are a fundamental statistical tools offering multiple advantages in data exploration and analysis.
+These techniques  allow for the understanding and quantification of relationships between variables.
+Regression analysis not only reveals the nature and strength of connections between dependent and independent variables, but also aids in prediction and model interpretation.
+It serves as a basis for decision-making by allowing insights into influential data points, model comparison, and assumption checking.
+Similarly, correlation analysis succinctly measures the degree and direction of association between two  variables, which gives a simple but effective way to summarizing their relationship \cite{Bewick_Cheek_Ball_2003}.
+All in all, these basic analyses provide crucial foundations for further statistical modeling, making them indispensable in the field of what variable affecting cycling will provide the greatest increase in bike share usage.
+Even though it is a simple technique, we are able to tell that there is a significant relationship between shared pathways, bicycle paths and separated pathways on the amount of bike share station usage.
+Which provides a solid foundation of evidence on how to improve cycling infrastructure in urban areas.
 
@@
 In the group of papers addressed, the multinomial logit (MNL) model was used to estimate the travel choice of bicycle for commuting \cite{10Zhao2013}.
+Multilevel models, unlike traditional regression approaches, offer several crucial advantages.
+Firstly, they accurately handle hierarchical data structures, avoiding underestimation of standard errors and overstating statistical significance by recognizing and accounting for group-level variability.
+Secondly, these models address substantive inquiries related to group effects, crucial in scenarios like transportation mode to work choices or identifying 'outlying' groups, providing insights into value-added effects at different levels.
+Thirdly, they enable simultaneous estimation of group effects and group-level predictors without confounding their impacts, which can't be separated in fixed effects models.
+Lastly, multilevel models permit inference to a population of groups, treating sampled groups as a random sample from a larger population, unlike fixed effects models, which restrict inferences solely to the sampled groups.
+These benefits collectively enhance the accuracy, depth, and scope of analyses, particularly in understanding complex hierarchical data structures and their effects \cite{Rasbash_2023}.
 

### 2023-12-15 Manuscript/Manuscript.tex
added explaination for poisson section

@@
 As well as a Binary Logit Proportional model "with the share of bike commuters in each city as the dependent variable".
-This paper analyzed the role of cycling infrastructure on commutership by bike in 90 of the largest 100 U.S.
+This paper analyzed the role of cycling infrastructure on commuter-ship by bike in 90 of the largest 100 U.S.
 cities.
 The OLS model is used for estimating coefficients of linear regression that describe the relationship between one or more quantitative independent variables and a dependent variable \cite{XLSTAT2023}.
-With p explanatory variables, the OLS regression model is:
-\[Y = \beta_{0}+\sum_{j=1,\dots, p}{\beta_{j}X_{j}}+\epsilon\]
+With p explanatory variables, the OLS regression model is given by equation \ref{eq:1}:
+\begin{equation} \label{eq:1}
+Y = \beta_{0}+\sum_{j=1,\dots, p}{\beta_{j}X_{j}}+\epsilon\
+\end{equation}
 
@@
 
-\subsection{Zero-inflated Poisson Regression Mode}
+\subsection{Zero-inflated Poisson Regression Model}
 \label{sec:pois}
@@
 The Poisson model is also used in \citet{9Cantisani2021} to "address the randomness due to the perception and decision of road users at the intersections", as their research is specifically on the crash likelihood of cyclists at roundabouts with different infrastructure types.
+Zero-inflated models, by assigning a non-zero probability of observing one or more occurrences (like crashes), avoid assuming inherent safety or non-safety in intersections.
+Due to these reasons, zero-inflated models are useful for analyzing crash count data.
+It's important to note that zero-inflated models are not as always superior for crash counts, but they are a viable option to consider for bike crash research \cite{Pew_Warr_Schultz_Heaton_2020}.
 

### 2023-12-15 Manuscript/Manuscript.tex
changed formating for embedded euqations

@@
 This model is used since the design is looking at collision rates pre to post instillation of bike lanes, and since the model allows for an over-abundance of zero counts in the data \cite{Giles2010}.
-The Poisson distribution's p.m.f is:
-\[P(Y=y) = \exp{(-\lambda)\lambda^{y}}/y!\]
+The model uses the Poisson distribution's p.m.f which is given my equation \ref{eq:2}:
+\begin{equation} \label{eq:2}
+P(Y=y) = \exp{(-\lambda)\lambda^{y}}/y!
+\end{equation}
 
@@
 
-Alongside this method, the cumulative curve method as used to extract traffic flow data from videos \cite{6Pu2017}. The basic model of the generalized linear model is:
-\[Y_{nx1} = X_{nxp}\beta_{px1}+\epsilon_{nx1}\]
+Alongside this method, the cumulative curve method as used to extract traffic flow data from videos \cite{6Pu2017}. Equation \ref{eq:3} gives the basic model of the generalized linear model:
+\begin{equation}\label{eq:3}
+Y_{nx1} = X_{nxp}\beta_{px1}+\epsilon_{nx1}
+\end{equation}
 Where the matrix of observed values of dependent variables is  $Y_{nx1}$, $X_{nxp}$ is the matrix of observed explanatory variables, $\beta_{px1} =$ is the matrix of coefficients for explanatory variables, and $\epsilon_{nx1}$ is the error.

### 2023-12-15 Manuscript/Manuscript.tex
added to discussion section

@@
 density are also shown in Figure ~\ref{fig:flow}, and reveals that the average bicycle speed decreases slightly as the density increases while  the flow is still increasing, and  when there is high density the variation of bicycle speed decreases a great deal.
-These results are also consistant across multople locations of urban streets.
+These results are also consistent across multiple locations of urban streets.
 \begin{figure}[hbt!]
@@
 
-The different types of cycling infrastructure, especially bike lanes, are shown in this body of research to have a significant impact on increasing cycling ridership.
+Investing in different types of cycling infrastructure, especially separated bike lanes, is shown in this body of research to have a significant impact on increasing cycling ridership.
 Whether it's an increase in bike-shares or commutership, this relationship is shown in the papers.
@@
 These sorts of results can lead to insights for urban planners when it comes to designing cities.
-\par
-
 Predictive models were also used, like binary regression models in \citet{2Yujun2019} to provide insight into all the factors influencing an individuals' choice to cycle for commuting.
@@
 
-Some future directions this field could go include focusing on more that just high socioeconomic areas.
+Some future directions this field could go include focusing on more than just high socioeconomic areas.
 This type of research has only really been done in affluent countries, likely because a lot of the research has been based off of bike-share systems.
@@
 Which would be beneficial to persuading policy makers towards creating more bike lanes and encouraging cycling.
+Further improvements in the field of statistical modeling to conduct bike lane research include using longitudinal studies, to track changes and trends, rather that just cross-sectional research at one point in time.
+\par
+
+In addition, there is a lack of spatial analysis models in the current body of research on cycling infrastructure.
+These models, particularly spatial regression, Geographically Weighted Regression (GWR), or spatial auto correlation analysis, would be valuable for understanding spatial patterns.
+For instance, clustering of bike lane usage, or identifying hot-spots of accidents and injuries along bike lanes \cite{Kanade_2022}.
+It could also be beneficial to include causal inference techniques when studying cycling infrastructure.
+These tools, like directed acyclic graphs and instrumental variable analysis, could be appropriate for investigating the causal impact of interventions or policy changes related to bike lane infrastructure on outcomes like safety or usage of the infrastructure \cite{Pearce_Lawlor_2016}.
 

### 2023-12-15 Manuscript/Manuscript.tex
edited conclusion section

@@
 In conclusion, this survey of statistical research on bike lanes offers a current snapshot of frequently used methods in the analysis of bike lanes.
+When working in this field of study, the choice of the best statistical model should consider the specific research objectives, the characteristics of the available data, and the assumptions of the model.
+Often, a combination of different models or methodologies may be more informative to comprehensively understand various aspects of bike lane-related phenomena.
+Consulting with experts in specific techniques and conducting exploratory data analysis can also guide the selection of the most appropriate statistical approach for a given bike lane research study.
+\par
+
 The significance of bike lanes in increasing cycling highlights the need for continued research and innovative statistical analysis to understand how to overcome the challenges of congestion, safety, and sustainability in transportation.
-This supports the efforts of enhancing cycling infrastructure for the benefits of individuals experiences while cycling and the betterment of entire communities.
+As shown in this summary paper, such analysis is critical to support the efforts of enhancing cycling infrastructure for the benefits of individuals experiences while cycling and the betterment of entire communities.
 

### 2023-12-15 Manuscript/Manuscript.tex
edited paper for grammar and spelling

@@
 \usepackage{booktabs}
-\usepackage{amsthm}
 \usepackage{graphicx}
@@
 \usepackage{enumitem}
-\usepackage{setspace}
-\usepackage{lipsum}
-\usepackage{siunitx}
 \usepackage[square,numbers]{natbib}
 \bibliographystyle{abbrvnat}
-
 \usepackage[]{lineno}
 \linenumbers*[1]
-
-% NOTE: To produce blinded version, replace "0" with "1" below.
-\newcommand{\blind}{0}
-
 \setlength{\linewidth}{3in}
-
 \providecommand{\keywords}[1]
@@
 }
+\begin{document}
 
-\begin{document}
-%\maketitle
-
-\if0\blind
-{
-  \title{\bf A Concise Survey on Statistical Analysis in Bike Lane Research}
+{\title{\bf A Concise Survey on Statistical Analysis in Bike Lane Research}
   \author{Zoe Macris\\
@@
 
-%\doublespace
-
 \begin{abstract}
@@
 Cycling plays an important role in society, and has taken a place as a sustainable and accessible mode of transportation and exercise.
-In order for cycling to be accessible for the most number of people, investments into bike lanes and cycling infrastructure have to be made.
-Through an examination of existing studies, we explore the current trends in method to show whether bike lanes have a statistically significant effect on cycling outcomes.
+In order for cycling to be accessible for the most number of people, investments into bike lanes and cycling infrastructure have been made.
+Through an examination of existing studies, we explore the current trends in statistical methods to show whether certain types of infrastructure have a significant effect on cycling outcomes.
 \end{abstract}
@@
 
-Given that they have been around for just over 200 years, the bicycle has  evolved considerably in it's utility to us as a society.
+Given that bikes have been around for just over 200 years, it is unsurprising that they have evolved considerably in their utility to us as a society in that time.
 Originally just for hobbyists, and inhibitively expensive, they are now one of the most accessible modes of transport \cite{BIKE2023}.
-The World Health Organizations recommendation is a minimum of 150 minutes of moderate aerobic activity per week \citep{WHO2020}.
-This is difficult to achieve in our sedentary society, but cycling is an excellent form of exercise that can also double as the mode of transport for commuting and completing daily tasks.
+Biking is an exceptional form of exercise and is a great way to achieve the World Health Organizations recommendation of a minimum of 150 minutes of moderate aerobic activity per week \citep{WHO2020}.
+This is difficult to achieve in our sedentary society, but doable with cycling since it is a form of exercise that can also double as the mode of transport for commuting and completing daily tasks.
 \par
@@
 
-In order to understand the research into bike lanes, these topics should be understood.
+In order to understand the significance of research into bike lanes, these following topics should be understood.
 
@@
 In recent years, there has been even more emphasis on sustainable and environmentally conscious transportation options in urban areas.
-Cycling fits the these criteria and has risen to prominence as a viable sustainable mode of transportation.
-It is a form of active transportation, which is defined as human powered, and thus does not release greenhouse gas emissions.
+Cycling fits these criteria and has risen to prominence as a sustainable mode of transportation.
+It is a form of active transportation, which is term defined as human powered, and thus does not release greenhouse gas emissions.
 Bikes also take up considerable less space and require significantly less infrastructure than cars as an added benefit.\par
-In order to promote cycling and make use of the benefits of alleviating traffic congestion, reduced emissions, and enhancing public health, it is necessary to plan and evaluate cycling infrastructure, and bike lanes more specifically.
-Statistical analysis can come into play here and help prove whether bike lanes make a significant impact on the propensity of people cycling and their safety while doing it.
+In order to promote cycling and make use of the benefits of alleviating traffic congestion, reduced emissions, and enhancing public health, it is necessary to plan and evaluate cycling infrastructure.
+Especially different forms of bike lanes, as this is commonly the only cycling infrastructure in the U.S.
+Statistical analysis comes into play here and can help prove whether bike lanes make a significant impact on the propensity of people cycling and their safety while doing it.
 
@@
 The visuals in Figure ~\ref{fig:bikelane}, show an even wider array of potential infrastructures.
-In the U.S., commonly seen types are Bicycle Awareness Zones, Informal On Road and Bicycle Lanes as seen in the images.
+In the U.S., commonly seen types are Bicycle Awareness Zones, Informal On Road and Bicycle Lanes.
 The supposition of much of the research analyzed here is that the more advanced the infrastructure is, the more likely people are to cycle \cite{1MateoBabiano2016}.\par
 
-\begin{figure}[hbt!]
+\begin{figure}[tbp]
     \centering
@@
 
-Shared roadways are where bicycle and automobile travel are allowed, all streets and roads other than controlled highways, are in this category.
+Shared roadways are where bicycle and automobile traffic are allowed, all streets and roads other than controlled highways, are in this category.
 They do not provide any added protection to cyclists, but a street's designation as shared roadway indicates to cyclists that there are advantages to using the route over alternatives \cite{CTDOT2023}.
@@
 \par
-The research in this survey focuses on the infrastructure of bicycle lanes, and whether they are sufficient to increase the propensities of people to cycle, and their safety while they are cycling.
+The bulk of research in this survey focuses on the infrastructure of bicycle lanes, and whether they are sufficient to increase the propensities of people to cycle, and their safety while they are cycling.
 
@@
 
-To conduct this comprehensive survey of statistical analyses on bike lanes, a search was conducted of academic databases such as Science Direct, ProQuest, MDPI, and PubMed.
-These searches were conducted through the University of Connecticut library of Databases to ensure they were papers that were a able to be accessed.
+To conduct this comprehensive survey of statistical analyses on bike lanes, a search was conducted of the academic databases Science Direct, ProQuest, MDPI, and PubMed.
+These searches were conducted through the University of Connecticut library of Databases to ensure that the full content of the papers could be viewed.
 Specific terms were used including "bike lane", "statistical analysis", and "cycling infrastructure" in order to identify relevant papers.
-The date range for literature was defined as 2012 to the present, upon evaluation of typical date range of the available literature.
+The date range for literature was defined as 2012 to the present, upon evaluation of the typical date range of the available literature.
 \par
@@
 A selection of eleven papers resulted from this, and the approach used to identify relevant data from the papers to be discussed in the survey paper was done as follows.
-The specific type of statistical analysis conducted in the paper was identified.
-Alongside the method and variables used by the researchers in the study.
-The results from the data collection are displayed in ~\ref{sec:results}.
+The specific type of statistical analysis conducted in the paper was identified, alongside the method and variables used by the researchers in the study.
+The results from the data collection are discussed in Section~\ref{sec:results}.
 
@@
 The results of the Spearman correlation of station usage and infrastructure type can be seen in Table ~\ref{table:MB}, where shared pathways, bicycle paths, connections, and separated pathways were shown to have a significant impact on PBSP usage.
-\par
 Other analyses used include Differences-in-Differences, Pearson's R correlation coefficient, Panel regressions, and Counterfactual based on control \cite{Karpinski2021}.
-These were used when the data being analyzed was usership of Boston's bike share program before and after the addition of bike lanes.
+These were used when the data being analyzed was user-ship of Boston's bike share program before and after the addition of bike lanes.
 
@@
 
-While a fairly simple technique, basic regression and correlation analyses are a fundamental statistical tools offering multiple advantages in data exploration and analysis.
+While a fairly simple technique, basic regression and correlation analyses are a fundamental statistical tool offering multiple advantages in data exploration and analysis.
 These techniques  allow for the understanding and quantification of relationships between variables.
@@
 Similarly, correlation analysis succinctly measures the degree and direction of association between two  variables, which gives a simple but effective way to summarizing their relationship \cite{Bewick_Cheek_Ball_2003}.
-All in all, these basic analyses provide crucial foundations for further statistical modeling, making them indispensable in the field of what variable affecting cycling will provide the greatest increase in bike share usage.
-Even though it is a simple technique, we are able to tell that there is a significant relationship between shared pathways, bicycle paths and separated pathways on the amount of bike share station usage.
+All in all, these basic analyses provide crucial foundations for further statistical modeling, making them indispensable in telling what variable affecting cycling will provide the greatest increase in bike share usage.
+Even though it is a simple technique, we are able to tell in \citet{1MateoBabiano2016} that there is a significant relationship between shared pathways, bicycle paths and separated pathways on the amount of bike share station usage.
 Which provides a solid foundation of evidence on how to improve cycling infrastructure in urban areas.
@@
 
-The binary logistic regression model is also used in this field of statistical research to predict the likelihood of a successful event occurring, like a high number of cycling routes close to green areas \cite{5CamposSnchez2019}.
+The binary logistic regression model is also used in the field of statistical research on bike lanes to predict the likelihood of a successful event occurring, like a high number of cycling routes close to green areas \cite{5CamposSnchez2019}.
 Binary logistic regression serves as an indispensable tool in predictive modeling due to its versatile applications and tailored approach to analyzing binary dependent variables.
@@
 non-default in loan scenarios.
-In the case of \citet{5CamposSnchez2019}, multiple variables are coded 1-0 in a binary fashion and can be seen in Figure ~\ref{fig:vartable}.
+In the case of \citet{5CamposSnchez2019}, multiple variables are coded 1-0 in a binary fashion and can be seen in Figure~\ref{fig:vartable}.
 \par
-\begin{figure}[hbt!]
-    \centering \includegraphics[width=1\textwidth]{vartable.png}
+
+\begin{figure}[tbp]
+    \centering \includegraphics[width=0.8\textwidth]{vartable.png}
     \caption{Variable Table for Binary Logistic Regression Model}
@@
 
-The paper from \citet{3Teixeira2020} uses Multiple Level Logistic Regression to analyze the impact of cycling in various cities with different cycling infrastructure on stress markers.
+Multiple Level Logistic Regression is used in the paper from \citet{3Teixeira2020} to analyze the impact of cycling infrastructure in different cities on stress markers.
 This analysis resulted in the data shown in Figure ~\ref{fig:stress}, of stress levels measured in different cities.
-The results of this research found that riding on a protected bike lane significantly reduces cyclists stress levels compared to cycling on the general use street.
-\begin{figure}[hbp!]
+The results of this research found that riding on a protected bike lane significantly reduces cyclists stress levels compared to cycling on a general use street.
+\begin{figure}[tbp]
     \centering
@@
 
-Two types of models were used in \citet{4Buehler2011}, a log-log Ordinary Least Square (OLS) model "with the dependent variable being the bike commuters per 10,000 population.
-As well as a Binary Logit Proportional model "with the share of bike commuters in each city as the dependent variable".
+Two types of models were used in \citet{4Buehler2011}, a log-log Ordinary Least Square (OLS) model with the dependent variable being the bike commuters per 10,000 population.
+As well as a Binary Logit Proportional model with the share of bike commuters from each city being the dependent variable.
 This paper analyzed the role of cycling infrastructure on commuter-ship by bike in 90 of the largest 100 U.S.
@@
 With p explanatory variables, the OLS regression model is given by equation \ref{eq:1}:
+
 \begin{equation} \label{eq:1}
@@
 
-In the group of papers addressed, the multinomial logit (MNL) model was used to estimate the travel choice of bicycle for commuting \cite{10Zhao2013}.
+In the group of papers addressed, the multinomial logit (MNL) model was most commonly used to estimate the travel choice of bicycle for commuting \cite{10Zhao2013}.
 Multilevel models, unlike traditional regression approaches, offer several crucial advantages.
@@
 Lastly, multilevel models permit inference to a population of groups, treating sampled groups as a random sample from a larger population, unlike fixed effects models, which restrict inferences solely to the sampled groups.
-These benefits collectively enhance the accuracy, depth, and scope of analyses, particularly in understanding complex hierarchical data structures and their effects \cite{Rasbash_2023}.
+These benefits collectively enhance the depth of the analyses, particularly in understanding complex hierarchical data structures and their effects \cite{Rasbash_2023}.
 
@@
 
-A different approach that was used in the research into bike lanes was to use a zero-inflated Poisson regression model to estimate the change in cycle-motor vehicle collisions \cite{8Bhatia2016}.
-This model is used since the design is looking at collision rates pre to post instillation of bike lanes, and since the model allows for an over-abundance of zero counts in the data \cite{Giles2010}.
-The model uses the Poisson distribution's p.m.f which is given my equation \ref{eq:2}:
+Another approach  used in the research into bike lanes is a zero-inflated Poisson regression model to estimate the change in cycle-motor vehicle collisions \cite{8Bhatia2016}.
+This model was used since the design is looking at collision rates pre to post instillation of bike lanes, and since the model allows for an over-abundance of zero counts in the data \cite{Giles2010}.
+The model uses the Poisson distribution's p.m.f which is given by equation \ref{eq:2}:
 \begin{equation} \label{eq:2}
@@
 Due to these reasons, zero-inflated models are useful for analyzing crash count data.
-It's important to note that zero-inflated models are not as always superior for crash counts, but they are a viable option to consider for bike crash research \cite{Pew_Warr_Schultz_Heaton_2020}.
+It is important to note that zero-inflated models are not always superior for crash counts, but they are a viable option to consider for bike crash research \cite{Pew_Warr_Schultz_Heaton_2020}.
 
@@
 
-The final method identified from the surveyed papers was to use the generalized linear model (GLM) to predict the vehicle delays caused by bicycle traffic versus other variables.
+The final method identified from the surveyed papers was the generalized linear model (GLM) being used to predict the vehicle delays caused by bicycle traffic versus other variables.
 The GLM has the benefit of being able to accommodate various types of response variables, including continuous, binary, count, and categorical data.
@@
 Where the matrix of observed values of dependent variables is  $Y_{nx1}$, $X_{nxp}$ is the matrix of observed explanatory variables, $\beta_{px1} =$ is the matrix of coefficients for explanatory variables, and $\epsilon_{nx1}$ is the error.
-Using this model is reported to help to understand how each factor contributed to the delay of cyclists on urban streets.
-In Figure ~\ref{fig:traffic}, the results are shown of results of the significance of multiple variables on vehicle delay, and it can be seen that with this method, bicycle and vehicle flow as well as the number of vehicle lanes, has a significant effect on vehicle delay.
+Using this model help us understand how each factor contributed to the delay of cyclists on urban streets.
+In Figure ~\ref{fig:traffic}, the results are shown of the significance of multiple variables on vehicle delay.
+It can be seen that with this method, bicycle and vehicle flow as well as the number of vehicle lanes, have a significant effect on vehicle delay.
 The results of flow vs.
-density are also shown in Figure ~\ref{fig:flow}, and reveals that the average bicycle speed decreases slightly as the density increases while  the flow is still increasing, and  when there is high density the variation of bicycle speed decreases a great deal.
+density are similarly shown in Figure ~\ref{fig:flow}, and reveals that the average bicycle speed decreases slightly as the density increases while the flow is still increasing, and  when there is high density the variation of bicycle speed decreases a great deal.
 These results are also consistent across multiple locations of urban streets.
-\begin{figure}[hbt!]
+\par
+
+\begin{figure}[tbp]
     \centering \includegraphics[width=1\textwidth]{BikeTrafficResults.png}
-    \caption{Results table from Research on Bicycle Traffic from Pu et al.}
+    \caption{Results table from Research on Bicycle Traffic from \citet{6Pu2017}}
     \label{fig:traffic}
@@
 
-\begin{figure}[hbt!]
+\begin{figure}[tbp]
     \centering \includegraphics[width=1\textwidth]{flowdensity.png}
-    \caption{Relationship between bicycle flow and density}
+    \caption{Relationship between bicycle flow and density from \citet{6Pu2017}}
     \label{fig:flow}
@@
 The findings from this survey paper show the multifaceted approaches being taken in the field of research into cycling infrastructure, and how important they are to encourage sustainable urban transportation.
-In this discussion section will include; key themes, criticisms, and potential future pathways for similar research.
+In this discussion section will include; important themes, criticisms, and potential future pathways for similar research.
 \par
@@
 Investing in different types of cycling infrastructure, especially separated bike lanes, is shown in this body of research to have a significant impact on increasing cycling ridership.
-Whether it's an increase in bike-shares or commutership, this relationship is shown in the papers.
+Whether it is an increase in bike-shares or commutership, this relationship is shown in the research.
 This is essential when it comes to appealing to policy makers and decision makers in communities to convince them to add cycling infrastructure to their area.
@@
 Studies like \citet{1MateoBabiano2016} show how effective simple methods like Spearman's correlation coefficient can be at revealing the impact of bike lanes on PBSP usage.
-These sorts of results can lead to insights for urban planners when it comes to designing cities.
+These sorts of results can lead to important ideas for urban planners when it comes to designing cities.
 Predictive models were also used, like binary regression models in \citet{2Yujun2019} to provide insight into all the factors influencing an individuals' choice to cycle for commuting.
@@
 
-Some future directions this field could go include focusing on more than just high socioeconomic areas.
-This type of research has only really been done in affluent countries, likely because a lot of the research has been based off of bike-share systems.
-Which leads into another point of improvements, where there could be better ways of collecting data on cyclists, as they are often excluding people who own their own bikes from the data.
+Some improvements this field could make include focusing on more than just high socioeconomic class areas.
+This type of research has only really been done in affluent countries, specifically in affluent areas, likely because much of the research has been based off of bike-share systems.
+Which leads into another point of criticism, where there could be better ways of collecting data on cyclists, as they are often excluding people who own and ride their own bikes from the data.
 Additionally, there is room for more cost-benefit analyses on the economic impact of investing in cycling infrastructure.
-When you create such infrastructure, there could be less congestion and damage to the automobile infrastructure.
-Which would be beneficial to persuading policy makers towards creating more bike lanes and encouraging cycling.
-Further improvements in the field of statistical modeling to conduct bike lane research include using longitudinal studies, to track changes and trends, rather that just cross-sectional research at one point in time.
-\par
+When you create well used bike lanes, there would then be less congestion and damage to automobile infrastructure.
+Focusing on this angle within bike lane research would be beneficial to persuading policy makers towards creating more bike lanes and encouraging cycling.
 
-In addition, there is a lack of spatial analysis models in the current body of research on cycling infrastructure.
-These models, particularly spatial regression, Geographically Weighted Regression (GWR), or spatial auto correlation analysis, would be valuable for understanding spatial patterns.
+Further improvements for the future of the field of research into cycling infrastructure include using longitudinal studies to track changes and trends, rather that just cross-sectional research at one point in time.
+In addition, there is a lack of spatial analysis models in the current body of research.
+These models, particularly spatial regression, Geographically Weighted Regression (GWR), and spatial auto correlation analysis, would be valuable for understanding spatial patterns.
 For instance, clustering of bike lane usage, or identifying hot-spots of accidents and injuries along bike lanes \cite{Kanade_2022}.

### 2023-12-15 Manuscript/Manuscript.tex
made last edits for final draft

@@
 
-{\title{\bf A Concise Survey on Statistical Analysis in Bike Lane Research}
+{\title{\bf A Concise Survey on Statistical Analysis Methods in Bike Lane Research}
   \author{Zoe Macris\\
@@
 
-\keywords{Bike Lanes, Regression Analysis, Binary Regression Models, Multiple Level Regression Analysis, Zero-Inflated Poisson, Generalized Linear Model}
+\keywords{Cycling Infrastructure, Regression Analysis, Binary Regression Models, Multiple Level Regression Analysis, Zero-Inflated Poisson, Generalized Linear Model}
 
